---
title: "Value boxes and gauges"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
# Import library and dataset

library(flexdashboard)
library(MASS)

library(dplyr)


#birthwt
birthwt2 <- within(birthwt, {
race <- factor(race, labels = c("white", "black", "other"))
ptl <- factor(ptl > 0) # premature labors
ftv <- factor(ftv) # physician visits
levels(ftv)[-(1:2)] <- "2+"
smoke <- factor(smoke>0)
ht <- factor(ht>0)
ui <- factor(ui>0)
})
birthwt2

#energy
energy<-read.csv("power_data.csv", header = TRUE, row.name="X")
x <- as.POSIXct(energy$Datetime, format="%Y-%m-%d %H:%M:%S")
year <- as.numeric(format(x, '%Y'))
month <- as.numeric(format(x, '%m'))
day <- as.numeric(format(x, '%d'))
hour <- as.numeric(format(x, '%H'))
energy<-cbind(energy, year, month, day, hour)
energy <- energy %>% mutate(Datetime = as.POSIXct(Datetime, format="%Y-%m-%d %H:%M:%S"))
energy<-energy[order(energy$Datetime), ]
rownames(energy) <- NULL
```

# Q1 Value boxes

## Row

### Low birth weight count

```{r}
low_birth_weight_count = sum(birthwt2$low == 1)
valueBox(low_birth_weight_count, 
         icon="fa-baby",
         color = "#ff9f80")
```

### Normal birth weight count

```{r}
normal_birth_weight_count = sum(birthwt2$low == 0)
valueBox(normal_birth_weight_count, 
         icon="fa-baby",
         color = "#cc3300")
```

## Row

### Low birth weight (black)

```{r}
low_birth_weight_black = sum(birthwt2$low == 0 & birthwt2$race == "black")
valueBox(low_birth_weight_black, 
         icon="fa-user",
         color = "#b3e0ff")
```

### Low birth weight (white)

```{r}
low_birth_weight_white = sum(birthwt2$low == 0 & birthwt2$race == "white")
valueBox(low_birth_weight_white, 
         icon="fa-user",
         color = "#002080")
```

### Low birth weight (other races)

```{r}
low_birth_weight_others = sum(birthwt2$low == 0 & birthwt2$race == "other")
valueBox(low_birth_weight_others, 
         icon="fa-user",
         color = "#008ae6")
```

## Row

### Low birth weight (ptl = FALSE)

```{r}
low_birth_weight_ptl_False = sum(birthwt2$low == 0 & birthwt2$ptl == FALSE)
valueBox(low_birth_weight_ptl_False, 
         icon="fa-person-pregnant",
         color = "#ffff00")
```

### Low birth weight (ptl =TRUE)

```{r}
low_birth_weight_plt_True = sum(birthwt2$low == 0 & birthwt2$ptl == TRUE)
valueBox(low_birth_weight_plt_True, 
         icon="fa-person-pregnant",
         color = "#ffffb3")
```


# Q2 Value Box 

## Row

### Total energy consumption during January 2010

```{r}
# Filter the data set for January 2010 and calculate the sum of POWER_MH
consumption_jan_2010 <- energy %>%
  filter(year == 2010, month == 1) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE))

valueBox(consumption_jan_2010$total_power, 
         icon = "fa-lightbulb-o",
         color = "#ffffb3")
```

### Energy consumption during May 2010

```{r}
consumption_may_2010 <- energy %>%
  filter(year == 2010, month == 5) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE))

valueBox(consumption_may_2010$total_power, 
         icon = "fa-lightbulb-o",
         color = "#ffffb3")

```

### Energy consumption during September 2010

```{r}
consumption_sep_2010 <- energy %>%
  filter(year == 2010, month == 9) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE))

valueBox(consumption_sep_2010$total_power, 
         icon = "fa-lightbulb-o",
         color = "#ffffb3")

```

# Q1 Gauges

## Row

### The percentage of mothers who had low infant birth (low = 1)

```{r}
# Calculate the percentage of mothers with low infant birth
proportion_low_infant_birth <- (sum(birthwt2$low == 1, na.rm = TRUE) * 100) / nrow(birthwt2)

gauge(proportion_low_infant_birth, min = 0, max = 100, symbol = "%", 
  gaugeSectors(
    success = c(0, 39),
    warning = c(40, 79),
    danger = c(80, 100)
  ))
```

### The percentage of mothers who had normal infant birth (low = 0)

```{r}
# Calculate the percentage of mothers with low infant birth
proportion_normal_infant_birth <- (sum(birthwt2$low == 0, na.rm = TRUE) * 100) / nrow(birthwt2)

gauge(proportion_normal_infant_birth, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        danger = c(0, 39),
        warning = c(40, 79),
        success = c(80, 100)
      ))
```

## Row

### The percentage of low birth weight for black race only

```{r}
# Calculate the percentage of black individuals with low infant birth
proportion_low_black <- (sum(birthwt2$race == 'black' & birthwt2$low == 1, na.rm = TRUE) * 100) / sum(birthwt2$race == 'black', na.rm = TRUE)

gauge(proportion_low_black, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))
```

### The percentage of low birth weight for white race only

```{r}
# Calculate the percentage of black individuals with low infant birth
proportion_low_white <- (sum(birthwt2$race == 'white' & birthwt2$low == 1, na.rm = TRUE) * 100) / sum(birthwt2$race == 'white', na.rm = TRUE)

gauge(proportion_low_white, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))
```

### The percentage of low birth weight for other races only

```{r}
# Calculate the percentage of black individuals with low infant birth
proportion_low_other <- (sum(birthwt2$race == 'other' & birthwt2$low == 1, na.rm = TRUE) * 100) / sum(birthwt2$race == 'other', na.rm = TRUE)

gauge(proportion_low_other, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))
```

# Q2 Gauges

## Row

### Percentage of Energy consumption in 2010 for January only

```{r}
prop_jan_energy_2010 <- energy %>%
  filter(year == 2010, month == 1) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE)) %>%
  mutate(percentage = (total_power / sum(energy$Power_MWH[energy$year == 2010], na.rm = TRUE)) * 100)
  
gauge(prop_jan_energy_2010$percentage, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))

```

### Percentage of Energy consumption in 2015 for January only

```{r}
prop_jan_energy_2015 <- energy %>%
  filter(year == 2015, month == 1) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE)) %>%
  mutate(percentage = (total_power / sum(energy$Power_MWH[energy$year == 2015], na.rm = TRUE)) * 100)

gauge(prop_jan_energy_2015$percentage, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))
```

### Percentage of Energy consumption in 2017 for January only

```{r}
prop_jan_energy_2017 <- energy %>%
  filter(year == 2017, month == 1) %>%
  summarise(total_power = sum(Power_MWH, na.rm = TRUE)) %>%
  mutate(percentage = (total_power / sum(energy$Power_MWH[energy$year == 2017], na.rm = TRUE)) * 100)

gauge(prop_jan_energy_2017$percentage, min = 0, max = 100, symbol = "%", 
      gaugeSectors(
        success = c(0, 39),
        warning = c(40, 79),
        danger = c(80, 100)
      ))

```
